```{r yield-summary-table, tab.cap = "Summary yield and _input_full_name_l_ rate data by zone"}
sum_tab

```

If the grower had not participated in the experiment, the chosen strategy would have been to apply _input_full_name_l_ uniformly across the field at _gc_rate_here_ _unit_here_ per acre.

The model predicts that this strategy was approximately _gc-opt-comp-txt-comes-here_.

For each zone, Figure \@ref(fig:status-quo-optimal-v) compares the differences in per-acre net revenues that would have resulted from different management strategies. (Net revenues equal revenues from soybean sales minus _input_full_name_l_ costs.) For Zone 1, the best estimates of the gain in net revenues when switching from the grower's chosen rate of _input_full_name_l_ _unit_here_ per acre would have been $`r get_pi_dif(pi_dif_test_zone, 1)`. Of course, as with any statistical data analysis, there cannot be 100% certainty that the actual difference in net revenues from the two management plans would end up being exactly $`r get_pi_dif(pi_dif_test_zone, 1)`. The black brackets centered over Zone 1's red circle illustrates that a 95% level of statistical confidence that the different in net revenues would have been between `r get_pi_ci_zone(pi_dif_test_zone, 1)`

A formal statistical test (called a t-test) _t-confidence-statement_1_ level of statistical confidence that net revenues would indeed be greater at the `r get_input(opt_gc_data, "opt_v", 1)`K rate than at the grower-chosen rate of _gc_rate_here_ _unit_here_ (t-value of `r get_t_value(pi_dif_test_zone, 1)`).

_rest-of-the-zones-here_

```{r status-quo-optimal-v, fig.cap = "Confidence intervals of the difference in net revenues under grower-chosen (_gc_rate_here_ _unit_here_) vs. optimal site-specific _seeding-or-application_ strategies by zone", fig.height = 4}

fig_data <- data.table::copy(pi_dif_test_zone) %>% 
  mutate(
    pi_dif_upper = point_est_dif + 1.96 * point_est_dif_se,
    pi_dif_lower = point_est_dif - 1.96 * point_est_dif_se
  )

g_pi_dif_zone <- ggplot(data = fig_data) +
  geom_point(
    aes(
      y = point_est_dif,
      x = zone_txt
    ), 
    size = 3, 
    color = "red"
  ) +
  geom_errorbar(
    aes(
    ymin = pi_dif_lower, 
    ymax = pi_dif_upper, 
    x = zone_txt
    ),
    size = 1
  ) +
  geom_hline(
    yintercept = 0, 
    color = "red", 
    size = 1.5
  ) +
  theme_bw() +
  ylab("Difference in Net Revenue ($/acre)") +
  theme(
    axis.title.x = element_text(size = 12, vjust = -1),
    axis.title.y = element_text(size = 12),
    axis.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    strip.text = element_text(size = 12)
  ) +
  fig_theme_nonsp

g_pi_dif_zone

```

Figure \@ref(fig:whole-field-profit-comp) shows confidence intervals of the gains in net revenues achieved by changing management strategies across the whole field.  The data and model's best estimate of that implementing the recommended site-specific _seeding-or-application_ strategy would result in a profit gain of approximately \$`r whole_profits_test[type_short == "ovg", round(point_est_dif, digits = 0)]` per acre.  The confidence interval shows that the evidence that the site-specific strategy is more profitable than the grower-chosen strategy is `r get_t_confidence_statement(whole_profits_test[type_short == "ovg", t])`. The data and model provide `r get_t_confidence_statement(whole_profits_test[type_short == "ovou", t])` evidence that the optimal variable rate strategy would result in greater profits than those from the optimal uniform rate strategy;  the point estimate of that profit difference is approximately \$`r whole_profits_test[type_short == "ovou", round(point_est_dif, digits = 0)]` per acre. The third confidence interval in the figure shows that the data and model `r get_t_confidence_statement(whole_profits_test[type_short == "oug", t])` evidence that the optimal uniform rate strategy of approximately `r round(unique(data_sf$opt_input_u), digits = 0)` _unit_here_ _input_full_name_l_ per acre would lead to higher profits than would the grower-chosen strategy of _gc_rate_here_ _unit_here_.  The point estimate of that profit difference is approximately \$`r whole_profits_test[type_short == "oug", round(point_est_dif, digits = 0)]`. 
