# Yield Data Processing

## Preparation

### Read datasets

```{r Reading-yield-data}
#--- yield ---#
yield_raw <- 
  here(
    "Data/Growers", 
    ffy,
    "Raw/yield-file-name-here.shp"
  ) %>% 
  st_read() %>% 
  #=== this took effect only when crs is missing ===#
  st_set_4326() %>% 
  st_transform_utm() %>%
  setnames(names(.), tolower(names(.))) %>% 
  mutate(yp_id = seq_len(nrow(.)))

```

```{r viz-yield-data}
tm_shape(yield_raw) +
  tm_dots() +
tm_layout_to_add 

```

## Various checks and consistency

### Change variable names

```{r Changing-variable-names}
if("time" %in% names(yield) & "isotime" %in% names(yield)) {
  yield <- dplyr::select(yield, - time) 
}

dict_yield <- dictionary[type == "yield", ]
col_list <- dict_yield[, column]

yield <- make_var_name_consistent(
  yield, 
  dict_yield 
)

yield <- dplyr::select(yield, matches(col_list)) %>% 
  mutate(yield_id := 1:nrow(.)) %>% 
  filter(!is.na(yield_vol))

if("offset" %in% names(yield) == FALSE){
  yield$offset <- 0
}

```

### Order by time

```{r eval = F}
setorder(yield, time)  
```

### Check units

This code assumes that if `distance` is in meter, then other variables (e.g., `width`) are also measured in meter.

```{r Checking-units-of-measurements}

dist_test <- yield %>% 
  cbind(., st_coordinates(.)) %>% 
  data.table() %>% 
  .[, dif_X := c(0, diff(X))] %>% 
  .[, dif_Y := c(0, diff(Y))] %>%  
  #--- distance in meter ---#
  .[, distance_r := sqrt(dif_X ^ 2 + dif_Y ^ 2)] %>%
  #--- dif in difference in meter and recorded distance ---#
  .[, dif_distance := abs(distance - distance_r)] %>%
  .[, dif_distance_conv := abs(conv_unit(distance, "ft", "m") - distance_r)]

# we want to see if the converted units from ft to meter are closer to the distance measured in r
if (mean(dist_test$dif_distance_conv, na.rm = TRUE) < mean(dist_test$dif_distance, na.rm = TRUE)){
  units <- "imperial"
}else{
  units <- "metric"
  }
```

### transform measurement unit

```{r Converting-units-to-metric}

if (units == "imperial") {
  yield <- yield %>%
    mutate(
      width = conv_unit(width, "ft", "m"),
      distance = conv_unit(distance, "ft", "m"),
      offset = conv_unit(offset, "ft", "m")
    )
}else{
  yield <- yield
}

```



## Group points by angle

```{r Grouping-yield-points-by-angle-and-detecting-sharp-turns-and-changes-of-rows}

yield_grouped <- group_points_sc(yield, by_var = NA, 30)  

```

Red points are the points that are recognized for making a sharp turn from their respective previous points.

```{r }
tm_shape(yield_grouped) +
    tm_dots(col = "blue") +
tm_shape(filter(yield_grouped, change_group == TRUE)) +
    tm_dots(col = "red", size = 0.1) +
tm_layout_to_add 

```

## Flag bad yield data points

```{r Flagging-outliers}
#/*----------------------------------*/
#' ## Yield-based
#/*----------------------------------*/
sd_factor <- 4

yield_grouped <- flag_bad_points(
    yield_grouped, 
    "yield_vol", 
    sd = sd_factor
  )

#/*----------------------------------*/
#' ## Speed-based
#/*----------------------------------*/
is_speed_available <- !all(is.na(yield_grouped$speed))

if (is_speed_available){
  yield_grouped %>%
  #=== speed-based ===#
  mutate(flag_bad = 
    ifelse(
      speed < 0.7 | speed > 8.2,
      1, 
      flag_bad
    )
  )
}

```

Yield distribution after cleaning (sd = `r sd_factor`)

```{r }
yield_grouped %>% filter(flag_bad == 0) %>% 
  pull(yield_vol) %>% 
  hist()
```

<br> 

`speed` vs `yield_vol`

```{r }
# now add speed if speed is missing 
if (is_speed_available) {
  ggplot(yield_grouped) +
    geom_point(aes(y = yield_vol, x = speed)) 
}

```

Which data points were dropped?

```{r }
tm_before <- tm_shape(yield_grouped) +
  tm_symbols(col = "yield_vol", size = 0.05) +
tm_layout_to_add 

tm_after <- tm_shape(filter(yield_grouped, flag_bad == 1)) +
  tm_symbols(col = "yield_vol", size = 0.05) +
tm_layout_to_add  

tmap_arrange(tm_before, tm_after)
```
 
```{r }
datasummary(
  yield_vol + width + speed + angle 
  ~ Mean + SD + median,
  data = yield_grouped
)  
```

## Yield data reduction when too dense

<!-- Example: Hord_F98_2020 -->

```{r Calculating-median-distance}
(med_distance <- yield$distance %>% median())
```

The following yield point reduction occurs when the medium distance between consecutive points is less than 1 meter.

```{r Reducing-to-smaller-number-of-points-if-dense}
#--- number of observations per reduced group ---#
# about 2 meter (many other yield data points have 2-meter gaps)

if (med_distance < 1){
  num_obs_rg <- floor(2 / (med_distance))

  yield_reduced_v <- reduce_points_v(
    data_sf = yield_grouped, 
    nobs_per_group = num_obs_rg, 
    var_interest = "yield_vol", 
    by_var = "group"
  )

} else {

  yield_reduced_v <- data.table(yield_grouped)

}

```

```{r }
cat(
  paste0("Before: ",  nrow(yield_grouped), " observations")
)

cat(
  paste0("After: ",  nrow(yield_reduced_v), " observations")
)

```


## Create polygons

```{r Creating-polygons-around-points-by-group}
#--- prepare parallel computation ---#
plan(multiprocess, workers = detectCores() - 2)

#--- create polygons ---#
all_polygons <- future_lapply(
  #--- list of groups to loop over ---#
  yield_reduced_v$group %>% unique(), 
  #--- make polygons by group ---#
  function(x) make_polygons(
    filter(yield_reduced_v, group == x)
  )
) %>% 
reduce(c) %>% 
st_as_sfc()   

#--- combine with the data ---#
yield_sf <- yield_reduced_v %>% 
  mutate(geometry = all_polygons) %>% 
  st_as_sf() %>% 
  st_set_crs(st_crs(yield)) %>% 
  #--- get rid of transition polygons by area ---#
  mutate(area = as.numeric(st_area(.))) %>% 
  filter(area <= median(area) * 3) %>% 
  mutate(yield_id = 1:nrow(.))
```

```{r }
tm_shape(yield_sf) +
  tm_polygons(col = "yield_vol", lwd = 0.05) +
tm_layout_to_add
```

## Flag polygons that went through previously visited parts of the field (overlap)

```{r Self-intersecting-polygons-for-overlap-detection}
#--- Find intersections among the polygons  ---#
intersections <- st_intersection(
  dplyr::select(yield_sf, yield_id, area),
  dplyr::select(yield_sf, yield_id)
) %>%
  mutate(int_area = as.numeric(st_area(.))) %>%
  data.table() %>% 
  .[yield_id > yield_id.1, ] %>% 
  .[, .(
      int_area = sum(int_area), 
      area = mean(area)
    ), 
    by = yield_id
  ]

#--- find and flag the polygons that visited previously visited area ---#
# 1/4 or more?
overlap_id_ls <- filter(intersections, int_area / area >= 1 / 10) %>%
  pull(yield_id) %>%
  unique()

#--- flag ---#
yield_polygons <- yield_sf %>%   
  filter(!st_is_empty(.)) %>% 
  mutate(overlap = ifelse(
    yield_id %in% overlap_id_ls,
    TRUE,
    FALSE
  ))

```

```{r }
cat(
  paste0(
    length(overlap_id_ls), 
    " were identified as polygons that visited previously-visited area with significant overlap."
  )
)
```

```{r dependson = "map-layout"}
tm_shape(yield_polygons) +
  tm_fill(
    col = "yield_vol", 
    alpha = 0.9
  ) +
  tm_borders(
    lwd = 0.3
  ) +
tm_layout_to_add

```

## Save the data

```{r saving-the-polygons}
here("Data/Growers", ffy, "Intermediate/yield_polygons.rds") %>% 
  saveRDS(yield_polygons, .) 

```

