# Process raw as-applied rate data

## Read in datasets

### As-applied data

```{r Reading-as-applied-n-data}

input_type <- "input_type_here"
input_form <- "input_form_here"
input_unit <- "input_unit_here"
reporting_unit <- "reporting_unit_here"
machine_width <- as.numeric("machine_width_here")

aa_input <-
  here(
    "Data/Growers", ffy, "Raw",
    "data_file_name_here"
  ) %>%
  #--- read the data ---#
  st_read() %>%
  st_set_4326() %>%
  st_transform_utm() %>%
  setnames(names(.), tolower(names(.))) %>%
  mutate(aa_id = 1:nrow(.))

is_aa_input_polygon <- any(st_geometry_type(aa_input) == "POLYGON")

if (is_aa_input_polygon) {
  aa_input <- close_unclosed(aa_input)
  #* we will merge this information later
  aa_input_poly <-
    aa_input %>%
    dplyr::select(aa_id, geometry)
  aa_input$geometry <- st_centroid(aa_input$geometry)
}

#--- get variable names ---#
aa_input_names <- names(aa_input)
```

```{r visialize-n-as-planted-data}
#--- visualize the points ---#
tm_shape(aa_input) +
  tm_dots()
```

### Medium distance of yield polygons

```{r }
#--- medium distance of yield polygons ---#
med_distance_yp <- get_med_dist(yield_polygons)
```

## Miscellaneous operations and various checks

### Change variable names

time variable needs to be dealt with separately

```{r }
if ("time" %in% names(aa_input) & "isotime" %in% names(aa_input)) {
  aa_input <- dplyr::select(aa_input, -time)
  time_available <- TRUE
}

dict_aa_input <- dictionary[type == input_type, ]
col_list <- dict_aa_input[, column]

aa_input <- make_var_name_consistent(
  aa_input,
  dict_aa_input
)

aa_input <-
  dplyr::select(
    aa_input,
    matches(c(col_list, "aa_id"))
  )
```

### Check units

This code assumes that if `distance` is in meter, then other variables (e.g., `width`) are also measured in meter.

```{r }
dist_test <- aa_input %>%
  dplyr::select(distance) %>%
  cbind(., st_coordinates(.)) %>%
  data.table() %>%
  .[, dif_X := c(0, diff(X))] %>%
  .[, dif_Y := c(0, diff(Y))] %>%
  #--- distance in meter ---#
  .[, distance_r := sqrt(dif_X^2 + dif_Y^2)] %>%
  #--- dif in difference in meter and recorded distance ---#
  .[, dif_distance := abs(distance - distance_r)] %>%
  .[, dif_distance_conv := abs(conv_unit(distance, "ft", "m") - distance_r)]

# we want to see if the converted units from ft to meter are closer to the distance measured in r
if (mean(dist_test$dif_distance_conv, na.rm = TRUE) < mean(dist_test$dif_distance, na.rm = TRUE)) {
  units <- "imperial"
} else {
  units <- "metric"
}
```

### Transform measurement unit

```{r }
if (units == "imperial") {
  aa_input <- aa_input %>%
    mutate(
      width = conv_unit(width, "ft", "m"),
      distance = conv_unit(distance, "ft", "m")
    )
} else {
  aa_input <- aa_input
}
```

### Convert input rate unit

If `N`, then base N rate is added as well.

```{r }
if (input_type == "N") {
  aa_input <-
    mutate(
      aa_input,
      input_rate = convert_N_unit(
        form = input_form,
        unit = input_unit,
        rate = input_rate,
        reporting_unit = reporting_unit
      )
    )
} else if (input_type == "S") {
  #--- seed rate conversion ---#
  if (any(aa_input$input_rate > 10000)) {
    #--- convert to K ---#
    aa_input <- mutate(aa_input, input_rate = input_rate / 1000)
  }
}
```

## Drop points in turns and group points by angle

Definitions:

+ dense: if the distance between points in the direction you are moving is very small


```{r }
recover_section_id <- FALSE # this gets updated if the use of points data is necessary
sectionid_var_available <- !all(is.na(aa_input$sectionid))


if (sectionid_var_available) { # if non-na section id variable is in the dataset
  #--- medium distance between aa_input points ---#
  med_distance_v <- get_med_dist_sec(aa_input)
  # === distance between sections ===#
  med_distance_h <- get_med_dist(aa_input)
  ratio <- med_distance_v / med_distance_h

  #--- number of sections ---#
  section_num <- data.table(aa_input)[, .(nobs = .N), by = .(angle)][, median(nobs)]

  if (ratio < 1.01 & ratio > 0.99) {
    # Note: if the ratio \sim 1, then it means we have only 1 observation per row
    section_num <- 1
    med_distance_v <- get_med_dist(aa_input)
  }
} else { # if sectionid variable is not present in the data

  # === find the number of the dominant number of the same rates ===#
  # Note: for non-section-controlled machines the dominant number should be 1
  dominant_rate_cluster_num <-
    data.table(aa_input)[, .(num_same_rate = .N), by = input_rate] %>%
    .[, .(num_num = .N), by = num_same_rate] %>%
    .[num_num == max(num_num), num_same_rate]

  # === estimate the machined width ===#
  # if not section controlled, get_med_dist() gets us
  # the median distance between points.
  # if section controlled, get_med_dist() gets us
  # the distance sections. This width times the number of sections has to be similar with the actual machine width.

  estimated_width <- dominant_rate_cluster_num * get_med_dist(aa_input)

  actual_machine_width <- conv_unit(machine_width, "ft", "m")

  if (
    dominant_rate_cluster_num > 1 &
      actual_machine_width * 0.95 < estimated_width &
      actual_machine_width * 1.05 > estimated_width
  ) {
    # this is the case where section level data is available, but section id is not available
    recover_section_id <- TRUE
    section_num <- 99 # (any positive number greater than 1 will do)
  } else { # no section control and

    #--- number of sections ---#
    section_num <- 1
  }
}
```

### Group points by changes in angle

```{r }

if (recover_section_id) { # if section id is missing even though the data is observed at the section level

  aa_input_grouped <- group_and_recover_section_id(aa_input) %>%
    st_as_sf()

  med_distance_v <- get_med_dist_sec(aa_input_grouped)
} else { # no section control of section control with section identifier
  if (section_num != 1) {
    #--- if section-controlled and more than one section observations at a time ---#
    aa_input_grouped <- group_points_sc(aa_input, "sectionid", angle_threshold = 30) %>%
      #--- remove observations with no group assigned ---#
      mutate(
        new_group = paste(group, sectionid, sep = "_")
      ) %>%
      arrange(id)
    #--- medium distance between aa_input points ---#
    med_distance_v <- get_med_dist_sec(aa_input_grouped)
  } else {
    #--- if only one observation at a time ---#
    aa_input_grouped <-
      group_points_sc(
        aa_input,
        by_var = NA,
        angle_threshold = 30
      ) %>%
      #--- remove observations with no group assigned ---#
      mutate(new_group = group)

    #--- medium distance between aa_input points ---#
    med_distance_v <- get_med_dist(aa_input_grouped)
  }
}
```

Red points are those that are recognized for making a sharp turn from their respective previous points.

```{r }
tm_shape(aa_input_grouped) +
  tm_dots(col = "blue") +
  tm_shape(filter(aa_input_grouped, change_group == TRUE)) +
  tm_dots(col = "red", size = 0.1) +
  tm_layout_to_add
```

## Intersect with the Trial Design and Flag Outliers by Treatment Block

### Import the trial design and visualize

**Read the trial design shape file**

```{r }
trd_polygons <-
  here(
    "Data/Growers", ffy, "TrialDesign",
    paste0(trial_info$tr_design_data, ".shp")
  ) %>%
  st_read() %>%
  st_transform(st_crs(aa_input_grouped)) %>%
  mutate(trd_id = 1:nrow(.))
```

**Visualization**
```{r }
# === vis ===#
tm_shape(trd_polygons) +
  tm_polygons(col = "Trt")

```

### Flag yield outliers by treatment block

This process uses a different criteria from that used for yield data.

+ Find the median of `input_rate` by treatment block
+ Flag observations as outliers if thier values deviate more than +- 10% from the median

```{r }

aa_input_trd <-
  aa_input_grouped %>%
  dplyr::select(aa_id, input_rate, group, geometry) %>%
  #* identify which yield point falls in which treatment block
  st_join(., trd_polygons) %>%
  #* order by yield id
  arrange(aa_id) %>%
  data.table() %>%
  #* flag outliers by treatment block
  nest_by(trd_id, group) %>%
  mutate(
    median_input_rate =
      median(data$input_rate, na.rm = TRUE)
  ) %>%
  mutate(data = list(
    mutate(data, ol_input_rate = ifelse(
      input_rate > median_input_rate * (1.1) | input_rate < median_input_rate * (0.9),
      1, 0
    ))
  )) %>%
  unnest() %>%
  data.table() %>%
  .[, .(aa_id, ol_input_rate)]

#* join with aa_input_grouped
aa_input_grouped <-
  left_join(aa_input_grouped, aa_input_trd, by = "aa_id")
```

**Show the points that are flagged as outliers**

1 indicates outliers.

```{r }
tm_shape(aa_input_grouped) +
  tm_dots(col = "ol_input_rate", style = "cat") +
  tm_layout_to_add
```



## Correct width if not right

```{r }

# /*----------------------------------*/
#' ## Width correction
# /*----------------------------------*/
if (section_num != 1) {

  # Note: this works as there are many observations at a single application time
  med_distance_h <- get_med_dist(aa_input_grouped)

  aa_input_grouped <- mutate(aa_input_grouped, width = med_distance_h)
} else {
  # if only one observation at a timestamp, use the reported width from the machine
  aa_input_grouped <- aa_input_grouped
}
```

## Vertically reduce points if dense (parallel to the direction the planter is moving)

When the points are too close to each other, creating polygons can fail because polygon creation depends on the angle from one point to the next.

```{r }
is_dense <- (med_distance_v * 2) < med_distance_yp

if (is_dense) {
  num_obs_rg <- ceiling(2 / (med_distance_v))

  aa_input_reduced_v <- reduce_points_v(aa_input_grouped, num_obs_rg, "input_rate", "new_group") %>%
    # === remove observations that has only observation per new_group ===#
    .[, .SD[.N != 1, ], by = new_group]
} else {

  # === Do not reduce ===#
  aa_input_reduced_v <-
    data.table(aa_input_grouped) %>%
    # === remove observations that has only observation per new_group ===#
    .[, .SD[.N != 1, ], by = new_group]
}
```

## Create polygons

```{r }
#--- prepare parallel computation ---#
plan(multiprocess, workers = detectCores() - 2)

#--- create polygons ---#
all_polygons <-
  future_lapply(
    #--- list of groups to loop over ---#
    aa_input_reduced_v$new_group %>% unique(),
    #--- make polygons by group ---#
    function(x) {
      make_polygons(
        filter(aa_input_reduced_v, new_group == x)
      )
    }
  ) %>%
  do.call("c", .) %>%
  st_as_sfc()

#--- combine with the data ---#
aa_input_sf <-
  aa_input_reduced_v %>%
  mutate(geometry = all_polygons) %>%
  st_as_sf() %>%
  st_set_crs(st_crs(aa_input)) %>%
  #--- get rid of transition polygons by area ---#
  mutate(area = as.numeric(st_area(.))) %>%
  filter(area <= median(area) * 3) %>%
  mutate(aa_input_id = 1:nrow(.)) %>%
  filter(!st_is_empty(.)) %>%
  dplyr::select(aa_input_id, input_rate, ol_input_rate)
```

```{r eval = is_aa_input_polygon}
aa_input_sf <- left_join(aa_input_poly, st_drop_geometry(aa_input_sf), by = "aa_id")
```

```{r }
tm_shape(aa_input_sf) +
  tm_polygons(
    lwd = 0.05,
    col = "input_rate"
  ) +
  tm_layout_to_add
```

**Check if polygon width is reasonable**

```{r }
tm_shape(aa_input_sf) +
  tm_polygons(
    lwd = 0.05,
    col = "red",
    alpha = 0.4
  ) +
  tm_layout_to_add
```

## Save the data

```{r }
here(
  "Data/Growers", ffy, "Intermediate",
  paste0("aa-", input_type, "-", input_form, ".rds")
) %>%
  saveRDS(aa_input_sf, .)
```
