# Combine yield and input datasets

## Preparation

### Read datasets

```{r }
#--- yield ---#
yield_polygons <- here("Data/Growers", ffy, "Intermediate/yield_polygons.rds") %>% 
  readRDS() %>%
  mutate(yield_area = as.numeric(st_area(.))) %>% 
  dplyr::select(yield_id, yield_area, yield_vol, flag_bad) %>% 
  filter(flag_bad == 0)

tm_shape(yield_polygons) +
  tm_fill(col = "yield_vol")

```

```{r }
input_polygons <- trial_info %>% 
  filter(process == TRUE) %>% 
  rowwise() %>% 
  mutate(
    input_file_name = here(
      "Data/Growers", 
      ffy, 
      "Intermediate", 
      paste0("as_applied_", input_type, ".rds")
    )
  ) %>% 
  mutate(
    input_polygons = list(
      readRDS(input_file_name)
    )
  ) 
   
``` 

```{r }
tm_inputs <- input_polygons %>% 
  mutate(
    tm_map = list(
      tm_shape(input_polygons) +
        tm_fill(
          col = "input_rate", 
          title = input_type
        )
    )
  )

tm_inputs$tm_map
```

```{r echo = F, eval = F}
tm_inputs <- input_polygons %>% 
  mutate(
    tm_map = list(
      tm_shape(input_polygons) +
        tm_fill(
          col = "red", 
          title = input_type,
          alpha = 0.4
        )
    )
  )

tm_inputs$tm_map

```

## Data alignment checks

```{r }
tm_alignment <- input_polygons %>% 
  mutate(
    tm_map = list(
      tm_shape(input_polygons) +
        tm_borders(lwd = 0.2) +
      tm_shape(st_centroid(yield_polygons)) +
        tm_dots(col = "blue", title = "Yield Points")
    )
  )

tm_alignment$tm_map 

```

## Filter out unreliable polygons

### Check the overlap and find area-weighted input rates

```{r }

input_pct <- input_polygons %>% 
  mutate(
    input_pct_data = list(
      intersect_yield_input(
        yield_polygons,
        input_polygons 
      )
    )
  ) %>% 
  dplyr::select(crop, input_type, input_pct_data) %>% 
  mutate(
    #=== visualize overlap ===#
    gg_overlap = list(
      ggplot(input_pct_data) +
      geom_histogram(aes(x = tot_sub_pct)) +
      ggtitle(
        paste(
          "Histogram of the percentage of yield polygons \n overlapping with", 
          input_type, 
          "polygons"
        )
      )     
    ),
    #=== visualize mix of rates ===#
    gg_dev = list(
      ggplot(input_pct_data) +
      geom_histogram(aes(x = dev_input_rate)) +
      ggtitle(
        paste(
          "Histogram of the deviation of ",
          input_type, 
          "\n to its mean by yield_id"
        )
      )     
    )
  )

```

```{r }
input_pct$gg_overlap

input_pct$gg_dev
```

### Filter out unreliable observations

```{r }
#=== convert max_dev_table if in ha instead of ac ===#
if(units == "metric"){
  max_dev_table %>%
    mutate(max_dev_allowed = max_dev_allowed*2.47105)
}
#=== yield data after removing unreliable inputs ===#
yield_input_data <- input_pct %>% 
  dplyr::select(crop, input_type, input_pct_data) %>% 
  left_join(max_dev_table, by = c("crop", "input_type")) %>% 
  mutate(
    input_pct_data = list(
      data.table::copy(input_pct_data) %>% 
      .[tot_sub_pct > 0.9 & tot_sub_pct < 1.1, ] %>% 
      .[dev_input_rate < max_dev_allowed, ] %>% 
      .[, .(yield_id, input_rate)] %>% 
      setnames(
        "input_rate",
        paste0(tolower(input_type), "_rate")
      )
    )
  ) %>% 
  pull(input_pct_data) %>% 
  reduce(inner_join, by = "yield_id") %>% 
  inner_join(yield_polygons, ., by = "yield_id")  

```


Red-filled polygons were dropped:

```{r dependson = "map-layout"}
tm_shape(st_as_sf(yield_polygons)) +
  tm_fill(col = "red") +
tm_shape(st_as_sf(yield_input_data)) +
  tm_fill(col = "green") +
tm_layout_to_add

```

## Yield grouping

### Assign group id

```{r }
yield_id_keep <- yield_input_data %>% 
  pull(yield_id)

distance_gap_allowed <- 6 # meter

group_id <- input_pct %>% 
  dplyr::select(crop, input_type, input_pct_data) %>% 
  left_join(max_dev_table, by = c("crop", "input_type")) %>% 
  mutate(
    group_change = list(
      left_join(yield_polygons, input_pct_data, by = "yield_id") %>% 
      filter(yield_id %in% yield_id_keep) %>% 
      cbind(., st_coordinates(st_centroid(.))) %>% 
      data.table() %>% 
      #--- push down X ---#
      .[, X_lag := data.table::shift(X, type = "lag")] %>% 
      #--- push down Y ---#
      .[, Y_lag := data.table::shift(Y, type = "lag")] %>% 
      #--- calculate the distance between consecutive points ---#
      .[, distance := sqrt((X_lag - X)^2 + (Y_lag - Y)^2)] %>% 
      #--- take care of the first ob ---#
      .[1, distance := 0] %>% 
      #--- 2 yield point gaps (2+1 multiplier) ---#
      .[, distance_gap := distance > distance_gap_allowed] %>% 
      .[, dif_input_rate := c(0, diff(input_rate))] %>% 
      .[, change_input_rate := abs(dif_input_rate) >= max_dev_allowed] %>% 
      .[, (change_input_rate | distance_gap)] 
    )
  ) %>% 
  ungroup() %>% 
  pull(group_change) %>% 
  Reduce("|", .) %>% 
  cumsum()

#/*~~~~~~~~~~~~~~~~~~~~~~*/
#' ### Approximate minimum length of subplots
#/*~~~~~~~~~~~~~~~~~~~~~~*/
med_distance <- get_med_dist(yield_polygons)  

# actual plot length will be longer than this
min_obs <- round(12 / med_distance) # 12 meter
max_obs <- round(20 / med_distance) # 24 meter

yield_group_data <- yield_input_data %>% 
  mutate(group_id = group_id + 1) %>% 
  data.table() %>% 
  #--- get the number of observations per group ---#
  .[, num_obs_group := .N, by = group_id] %>% 
  #--- get the cumulative number of observations ---#
  .[, dummy := 1] %>% 
  .[, cum_num := cumsum(dummy), by = group_id] %>% 
  #--- remove observations that belong to a group with less than mim_obs ---#
  .[num_obs_group >= min_obs, ]


```

### Assign subgroup id

```{r }
all_data_ls <- list()

for (i in min_obs:max_obs) {

  if (i == min_obs){

    temp_sub_id <- data.table::copy(yield_group_data) %>% 
      .[, sub_group_id := (cum_num - 1) %/% i  + 1] 

    group_ls <- temp_sub_id %>% 
      .[, num_obs_sub := .N, by = .(group_id, sub_group_id)] %>% 
      .[, too_small := num_obs_sub < min_obs] %>% 
      .[, drop := any(too_small), by = group_id] %>% 
      .[drop == FALSE, group_id] %>% unique()

    all_data_ls[[paste(i)]] <- temp_sub_id[group_id %in% group_ls, ] 

    bad_guys <- temp_sub_id[!(group_id %in% group_ls), ]

  } else {

    temp_sub_id <- data.table::copy(bad_guys) %>% 
      .[, sub_group_id := (cum_num - 1) %/% i  + 1] 

    group_ls <- temp_sub_id %>% 
      .[, num_obs_sub := .N, by = .(group_id, sub_group_id)] %>% 
      .[, too_small := num_obs_sub < min_obs] %>% 
      .[, drop := any(too_small), by = group_id] %>% 
      .[drop == FALSE, group_id] %>% unique()

    all_data_ls[[paste(i)]] <- temp_sub_id[group_id %in% group_ls, ] 

    bad_guys <- temp_sub_id[!(group_id %in% group_ls), ]

  }

  if(nrow(bad_guys) == 0){
    break
  }
     
}

input_var <- pluck(input_pct, "input_type") %>% 
  tolower(.) %>% 
  paste0(., "_rate")

yield_sf <- all_data_ls %>% 
  rbindlist() %>% 
  .[, obs_id := .GRP, by = .(group_id, sub_group_id)] %>% 
  st_as_sf() %>% 
  dplyr::select(
    any_of(c(
      c("yield_id", "yield_vol", "obs_id"), 
      input_var
    ))
  )

```

```{r }
cat(
  paste0(
    "There are ", 
    yield_sf$obs_id %>% unique() %>% length(),
    " observations."
  )
) 
```

Please note that each of the polygons are not observations units here.

```{r dependson = "map-layout"}
#--- yield map ---#
tm_shape(yield_sf) +
  tm_fill(col = "yield_vol") +
tm_layout_to_add
```

```{r }
lapply(
  input_var, 
  function(x) {
    tm_shape(yield_sf) +
      tm_fill(col = x)
  }
)  
```

```{r dependson = "map-layout"}
#--- yield map ---#
tm_shape(yield_sf) +
  tm_fill(col = "obs_id", style = "cont") +
tm_layout_to_add
```

## Save

```{r }
saveRDS(yield_sf, file = here("Data", "Growers", ffy, "Intermediate/yield_group_by_obs.rds"))
```


