---
title: "Report for Non-experimental Data: Topography, SSURGO, Weather, and Others"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: true
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
td {  /* Table  */
  font-size: 16px;
}
h1.title {
  font-size: 56px;
}
h1 { /* Header 1 */
  font-size: 48px;
}
h2 { /* Header 2 */
    font-size: 36px;
}
h3 { /* Header 3 */
  font-size: 24px;
}
code.r{ /* Code block */
    font-size: 16px;
}
</style>

```{r setup, cache = F, echo = F}
library(knitr)
knitr::opts_chunk$set(
  cache = FALSE,
  echo = TRUE,
  error = TRUE,
  warning = FALSE,
  cache.lazy = FALSE,
  message = FALSE,
  fig.width = 12,
  fig.height = 12
)
```

```{r packages, cache = FALSE}
# === packages ===#
library(raster)
library(sf)
library(here)
library(ggplot2)
library(tmap)
library(patchwork)
library(measurements)
library(scam)
library(parallel)
library(stars)
library(elevatr)
library(future.apply)
library(dplyr)
library(tidyverse)
library(modelsummary)
library(jsonlite)
library(data.table)
library(exactextractr)
library(future.apply)
```

```{r preparations, cache = F}
source(
  "https://github.com/tmieno2/OnFarmExperiments/blob/master/Functions/prepare.R?raw=TRUE",
  local = TRUE
)

#--- github ---#
source("https://raw.githubusercontent.com/brittanikedge/DIFM/main/Functions.R")

#--- define field-year ---#
ffy <- "field-year-here"

#--- read the variable name dictionary ---#
dictionary <-
  fromJSON(
    file.path(
      here("Data", "CommonData"),
      "variable_name_dictionary.json"
    ),
    flatten = TRUE
  ) %>%
  data.table()

#--- define field parameters ---#
trial_info <- get_trial_parameter(ffy)
input_trial_data <- trial_info$input_data_trial
```

```{r set-root-dir}
opts_knit$set(root.dir = here("Data", "Growers", ffy))
```

```{r map-layout, cache = TRUE}
tm_layout_to_add <-
  tm_layout(
    legend.outside = "TRUE",
    frame = FALSE,
    legend.title.size = 2,
    legend.text.size = 1.5
  )
```

# Topography data

## Download elevation data for the area of interest

```{r }
# === trial design file ===#
boundary_sf <-
  here(
    "Data", "Growers", ffy, "TrialDesign",
    paste0(get_trial_parameter(ffy)$tr_design_data, ".shp")
  ) %>%
  st_read() %>%
  st_set_4326() %>%
  st_transform_utm() %>%
  st_bbox() %>%
  st_as_sfc() %>%
  st_as_sf()

boundary_sp <- as(boundary_sf, "Spatial")

dem <-
  get_elev_raster(
    boundary_sp,
    clip = "locations",
    z = 14
  )

# === visualization ===#
tm_shape(dem) +
  tm_raster()

```

## Calculate topographic variables

### Slope and Aspect
Use the `terrain()` function from raster to get slope and aspect:

```{r }
dem_sa <- terrain(dem, opt = c("slope", "aspect"))
names(dem_sa) <- c("slope", "aspect")
```

### Curvature

Use the `curvature()` function from spatialEco to get curvature:

```{r }
curv <- curvature(dem, s = 5)
names(curv) <- "curv"
```

### TPI

Use the `tpi()` function from the `spatialEco` to get terrain position index:

```{r }
tpi <- tpi(dem, s = 5)
names(tpi) <- "tpi"
```

### TWI

Use the `upslope.area()` function from the `dynatopmodel` to get terrain wetness index:

```{r }
contrib_area <- upslope.area(dem, atb = TRUE)
twi <- contrib_area$atb
names(twi) <- c("twi")
```

## Organize the datasets and save

```{r }
#--- Stack all the rasters together ---#
topo <-
  stack(dem, dem_sa, curv, twi, tpi) %>%
  st_as_stars() %>%
  split(3)

names(topo)[1] <- "elevation"

#--- save the data ---#
saveRDS(topo, here("Data", "Growers", ffy, "Intermediate/topography.rds"))
```

## Remove the original DEM files

```{r eval = F}
list.files("Raw", full.names = TRUE) %>%
  .[str_detect(., "USGS")] %>%
  unlink()
```

## Visualization of the data

```{r }
lapply(
  names(topo),
  function(x) {
    tm_shape(topo[x, ]) +
      tm_raster() +
      tm_layout(
        legend.title.size = 3
      )
  }
)
```

# SSURGO data

## Download SSURGO data for the area of interest

```{r extra-package, cache = F}
library(soilDB)
```

```{r }
boundary_sf <-
  here(
    "Data", "Growers", ffy, "TrialDesign",
    paste0(get_trial_parameter(ffy)$tr_design_data, ".shp")
  ) %>%
  st_read() %>%
  st_set_4326() %>%
  st_transform_utm() %>%
  st_bbox() %>%
  st_as_sfc() %>%
  st_as_sf()

boundary_sp <- as(boundary_sf, "Spatial")

#--- download SSURGO ---#
vars <- c("sandtotal_r", "silttotal_r", "claytotal_r", "awc_r", "om_r", "dbovendry_r")
ssurgo_data <- get_ssurgo_props(boundary_sp, vars = vars)

```

## Visualize

```{r }
lapply(
  vars,
  function(x) {
    copy(ssurgo_data) %>%
      setnames(x, "var") %>%
      ggplot(data = .) +
      geom_sf(aes(fill = var)) +
      scale_fill_gradient(name = x)
  }
)
```

## Save

```{r }
saveRDS(ssurgo_data, here("Data", "Growers", ffy, "Intermediate/ssurgo.rds"))
```

# Weather data

## Download PRISM data for the area of interest

```{r extra-package-weather, cache = F}
library(daymetr)
library(lubridate)
```

```{r }
#--- get the boundary ---#
boundary_sf <-
  here(
    "Data", "Growers", ffy, "TrialDesign",
    paste0(get_trial_parameter(ffy)$tr_design_data, ".shp")
  ) %>%
  st_read() %>%
  st_set_4326() %>%
  st_transform_utm() %>%
  st_bbox() %>%
  st_as_sfc() %>%
  st_as_sf()

centroid <-
  boundary_sf %>%
  st_transform(4326) %>%
  st_centroid() %>%
  st_coordinates()

if (trial_info$year == as.numeric(format(Sys.time(), "%Y"))) {
  end_year <- trial_info$year - 1
} else {
  end_year <- trial_info$year
}

#--- download Daymet ---#
# goes 20 years back from the current year
temp_daymet <-
  download_daymet(
    lat = centroid[1, "Y"],
    lon = centroid[1, "X"],
    start = end_year - 20,
    end = end_year
  ) %>%
  .$data %>%
  data.table()
```

Go [here](https://daymet.ornl.gov/overview) and see the "Model Outputs and Data Products" for variable descriptions.

+ Day length (dayl,  s/day): Duration of the daylight period in seconds per day. This calculation is based on the period of the day during which the sun is above a hypothetical flat horizon

+ Precipitation (prcp,  mm/day): Daily total precipitation in millimeters per day, sum of all forms converted to water-equivalent. Precipitation occurrence on any given day may be ascertained.

+ Shortwave radiation (srad, W/m2): Incident shortwave radiation flux density in watts per square meter, taken as an average over the daylight period of the day. NOTE: Daily total radiation (MJ/m2/day) can be calculated as follows: ((srad (W/m2) * dayl (s/day)) / l,000,000)

+ Snow water equivalent (swe, kg/m2): Snow water equivalent in kilograms per square meter. The amount of water contained within the snowpack.

+ Maximum air temperature (tmax, degrees C): Daily maximum 2-meter air temperature in degrees Celsius.

+ Minimum air temperature (tmin, degrees C): Daily minimum 2-meter air temperature in degrees Celsius.

+ Water vapor pressure (vp, Pa): Water vapor pressure in pascals. Daily average partial pressure of water vapor.

```{r }
temp_daymet <-
  temp_daymet %>%
  setnames(
    names(.)[-c(1, 2)],
    c(
      "day_length",
      "precipitation",
      "solar_radiation",
      "shortwave_radiation",
      "tmax",
      "tmin",
      "vapor_pressure"
    )
  ) %>%
  .[, date := as.Date(paste(year, yday, sep = "-"), "%Y-%j")] %>%
  .[, `:=`(
    month = month(date),
    day = day(date)
  )]
```

## Save

```{r }
saveRDS(temp_daymet, here("Data", "Growers", ffy, "Intermediate/weather_daymet.rds"))
```



