# Topography data

## Preparation

```{r additional-packages}
library(sf)
library(sp)
library(raster)
library(stars)
library(elevatr)
library(spatialEco)
library(dynatopmodel)
library(terra)
library(tmap)
```

## Download elevation data for the area of interest

```{r }
#--- read the boundary file ---#
boundary_file <- here("Data", "Growers", ffy, "Raw/boundary.shp") 

td_file <- here("Data", "Growers", ffy, "TrialDesign") %>% 
  list.files(full.names = TRUE) %>% 
  .[str_detect(., "shp")] %>% 
  .[str_detect(., "trial-design")] %>% 
  #=== get the first one in case we have two separate files ===#
  .[1]

if (file.exists(boundary_file)) {
  boundary_sf <- st_read(boundary_file) %>%
  st_set_4326() %>%
  st_transform_utm() %>%
  st_bbox() %>%
  st_as_sfc() %>%
  st_as_sf()
} else if (file.exists(td_file)) {
  boundary_sf <- st_read(td_file) %>%
  st_set_4326() %>%
  st_transform_utm() %>%
  st_bbox() %>%
  st_as_sfc() %>%
  st_as_sf()
}

boundary_sp <- as(boundary_sf, "Spatial")

dem <- get_elev_raster(
  boundary_sp,
  clip = "locations",
  z = 14
)

```

```{r }
tm_shape(dem) +
  tm_raster()
```

## Calculate topographic variables

### Slope and Aspect
Use the `terrain()` function from raster to get slope and aspect:

```{r }
dem_sa <- terrain(dem, opt = c("slope", "aspect"))
names(dem_sa) <- c("slope", "aspect")
```

### Curvature

Use the `curvature()` function from spatialEco to get curvature:

```{r }
curv <- curvature(dem, s = 5)
names(curv) <- "curv"
```

### TPI

Use the `tpi()` function from the `spatialEco` to get terrain position index:

```{r }
tpi <- tpi(dem, s = 5)
names(tpi) <- "tpi"
```

### TWI

Use the `upslope.area()` function from the `dynatopmodel` to get terrain wetness index:

```{r }
contrib_area <- upslope.area(dem, atb = TRUE)
twi <- contrib_area$atb
names(twi) <- c("twi")
```

## Organize the datasets and save

```{r }
#--- Stack all the rasters together ---#
topo <- stack(dem, dem_sa, curv, twi, tpi) %>%
  st_as_stars() %>%
  split(3)

#--- save the data ---#
saveRDS(topo, here("Data", "Growers", ffy, "Intermediate/topography.rds"))
```

## Remove the original DEM files

```{r eval = F}
list.files("Raw", full.names = TRUE) %>%
  .[str_detect(., "USGS")] %>%
  unlink()
```

## Visualization of the data

```{r }
lapply(
  names(topo),
  function(x) {
    tm_shape(topo[x, ]) +
      tm_raster() +
      tm_layout(
        legend.title.size = 3
      )
  }
)
```


