# Weather data

## Download PRISM data for the area of interest

```{r extra-package-weather, cache = F}
library(daymetr)
library(lubridate)
```

```{r }
#--- get the boundary ---#
boundary_sf <- st_read("Raw/boundary.shp") %>%
  st_transform(4326) %>%
  st_bbox() %>%
  st_as_sfc() 

centroid <- boundary_sf %>% 
  st_centroid() %>% 
  st_coordinates()

year <- field_data %>% 
  .[field_year == ffy, year]
  
#--- download Daymet ---#
# goes 20 years back from the current year
temp_daymet <- download_daymet(
    lat = centroid[1, "Y"],
    lon = centroid[1, "X"],
    start = year - 20,
    end = year 
  ) %>% 
  .$data %>% 
  data.table()
```

Go [here](https://daymet.ornl.gov/overview) and see the "Model Outputs and Data Products" for variable descriptions.

+ Day length (dayl,  s/day): Duration of the daylight period in seconds per day. This calculation is based on the period of the day during which the sun is above a hypothetical flat horizon

+ Precipitation (prcp,  mm/day): Daily total precipitation in millimeters per day, sum of all forms converted to water-equivalent. Precipitation occurrence on any given day may be ascertained.

+ Shortwave radiation (srad, W/m2): Incident shortwave radiation flux density in watts per square meter, taken as an average over the daylight period of the day. NOTE: Daily total radiation (MJ/m2/day) can be calculated as follows: ((srad (W/m2) * dayl (s/day)) / l,000,000)

+ Snow water equivalent (swe, kg/m2): Snow water equivalent in kilograms per square meter. The amount of water contained within the snowpack.

+ Maximum air temperature (tmax, degrees C): Daily maximum 2-meter air temperature in degrees Celsius.

+ Minimum air temperature (tmin, degrees C): Daily minimum 2-meter air temperature in degrees Celsius.

+ Water vapor pressure (vp, Pa): Water vapor pressure in pascals. Daily average partial pressure of water vapor.

```{r }
temp_daymet <- temp_daymet %>% 
  setnames(
    names(.)[-c(1,2)], 
    c(
      "day_length",
      "precipitation",
      "solar_radiation",
      "shortwave_radiation",
      "tmax",
      "tmin",
      "vapor_pressure"
    )
  ) %>% 
  .[, date := as.Date(paste(year, yday, sep = "-"), "%Y-%j")] %>% 
  .[, `:=`(
    month = month(date),
    day = day(date)
  )] 
```

## Save

```{r }
saveRDS(temp_daymet, "Intermediate/weather_daymet.rds")
```
