---
title: "Trial Design Generation Report for _field-year-here_"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: true
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 20px;
  }
td {  /* Table  */
  font-size: 16px;
}
h1.title {
  font-size: 56px;
}
h1 { /* Header 1 */
  font-size: 48px;
}
h2 { /* Header 2 */
    font-size: 36px;
}
h3 { /* Header 3 */
  font-size: 24px;
}
code.r{ /* Code block */
    font-size: 16px;
}
</style>

```{r setup, cache = F, echo = F}
library(knitr)
knitr::opts_chunk$set(
  cache = FALSE,
  echo = TRUE,
  error = TRUE,
  warning = FALSE,
  cache.lazy = FALSE,
  message = FALSE,
  fig.width = 12, 
  fig.height = 12
)
```

```{r packages, cache = FALSE}
# === packages ===#
library(pracma)
library(furrr)
library(exactextractr)
library(sp)
library(sf)
library(here)
library(agricolae)
library(lwgeom)
library(measurements)
library(stringr)
library(tmap)
library(raster)
library(tidyverse)
library(data.table)
library(purrr)
library(DT)
```

```{r preparations, cache = F}
source(
  "https://github.com/tmieno2/DIFM/blob/master/Functions/prepare.R?raw=TRUE",
  local = TRUE
)

#--- github ---#
source("https://raw.githubusercontent.com/brittanikedge/DIFM/main/Functions.R")

#--- define field-year ---#
ffy <- "_field-year-here_"  
json_file <- "_json-file-here_"

```

```{r map-layout, cache = TRUE}
tm_layout_to_add <- tm_layout(
  legend.outside = "TRUE",
  frame = FALSE,
  legend.title.size = 2,
  legend.text.size = 1.5
)
```

# Get and Check Experiment Parameters

```{r }
trial_data <- 
readRDS(
  here("Data", "Growers", ffy, "TrialDesign/trial_data.rds")
) 
```   

## Rates specifications

```{r }
dplyr::select(
  trial_data, 
  gc_rate, 
  min_rate, 
  max_rate, 
  design_type,
  num_levels,
  max_jump
) %>% 
kable()

```


## ab-line specification

```{r }
dplyr::select(
  trial_data,
  plot_heading, 
  ab_line_type
) %>% 
kable()
  
```

## plot specification

```{r }
dplyr::select(
  trial_data,
  input_plot_width, 
  machine_width,
  section_num,
  section_width,
  headland_length,
  side_length
) %>% 
kable()
  
```

# Create Trial Designs

## Read boundary and ab-line

```{r }
# ffy <- "Wendte_LaueLib80_2020"
# ffy <- "Boeckner_134n_2017"
# ffy <- "Bohnhoff_Adams_2018"
# ffy <- "Holzwart_Holzwart_2021"

#/*=================================================*/
#' # Field boundary
#/*=================================================*/
boundary_file <- "_boundary-file-here_"

field_sf <- get_shp_name(ffy, "TrialDesign", boundary_file) %>% 
  st_read() %>% 
  make_sf_utm() %>% 
  st_combine()

field_bbox <- st_bbox(field_sf) 

field_len_cross <- sqrt(
  (field_bbox["xmax"] - field_bbox["xmin"]) ^2 +
  (field_bbox["ymax"] - field_bbox["ymin"]) ^2 
)

#/*=================================================*/
#' # Plot-heading and other parameters
#/*=================================================*/

trial_data_pa <- 
trial_data  %>% 
#=== whether to lock or not ===#
mutate(lock_ab_line = 
  ab_line_type == "lock"
) %>% 
#=== input with ab-line lock first ===#
arrange(desc(lock_ab_line)) %>%   
mutate(input_id = seq_len(nrow(.))) %>% 
rowwise() %>% 
mutate(line_edge_id = NA) %>% 
#=== heading sf ===#
mutate(ab_sf = list(
  get_shp_name(ffy, "TrialDesign", paste0(plot_heading, ".shp")) %>% 
  st_read() %>% 
  make_sf_utm() 
)) %>% 
mutate(ab_sf = list(
  if ("POINT" %in% st_geometry_type(ab_sf)) {
    make_heading(ab_sf, field_sf)
  } else {
    #=== pick only the first one ===#
    ab_sf[1, ]
  }
)) %>% 
#=== make ab-line longer ===#
mutate(ab_sf = list(
  st_extend_line(
    st_geometry(ab_sf), 
    field_len_cross / as.numeric(st_length(ab_sf))
  )
))

if (
  nrow(trial_data_pa) > 1 & 
  trial_data_pa[2, ]$ab_line_type != "lock"
) {
  create_plot_edge_line <- TRUE
} else {
  create_plot_edge_line <- FALSE
}

```

```{r }
trial_data_pa %>% 
mutate(gg_ab_line = list(
  ggplot() +
    geom_sf(data = field_sf) +
    geom_sf(data = ab_sf, col = "red") 
)) %>% 
pluck("gg_ab_line")

```

## Make experiment plots

```{r }
#/*----------------------------------*/
#' ## Create experimental plots
#/*----------------------------------*/
#=== get the first one of the two if more than one ===#
# plot_width <- trial_data_first$input_plot_width[[1]]
# harvester_width <- trial_data_first$harvester_width[[1]]
# ab_line <- trial_data_first$ab_sf[[1]]
# ab_line_data <- trial_data_first$base_ab_lines_data[[1]]
# ab_line_type <- trial_data_first$base_ab_lines_data[[1]]
# machine_width <- trial_data_first$machine_width[[1]]
# min_plot_length <- trial_data_first$min_plot_length[[1]]
# max_plot_length <- trial_data_first$max_plot_length[[1]]
# section_num <- trial_data_first$section_num[[1]]
# headland_length <- trial_data_first$headland_length[[1]]
# side_length <- trial_data_first$side_length[[1]]
# second_input <- FALSE
# ab_line_type <- trial_data_first$ab_line_type[[1]]
# field = field_sf

num_unique_plot_width <-  
trial_data_pa$input_plot_width %>% 
unique() %>% 
length()

#/*=================================================*/
#' # First input
#/*=================================================*/
# ab_lines_data <- trial_data_first$ab_lines_data[[1]]

trial_data_first <- 
trial_data_pa[1, ] %>% 
mutate(base_ab_lines_data = list(
  prepare_ablines(
    ab_line = ab_sf, 
    field = field_sf, 
    plot_width = input_plot_width
  ) 
)) %>% 
mutate(exp_data = list(
  make_trial_plots(
    field = field_sf, 
    #--- by default uses the first one ---#
    ab_lines_data = base_ab_lines_data, 
    ab_line_type = ab_line_type,
    plot_width = input_plot_width, 
    machine_width = machine_width, 
    harvester_width = harvester_width, 
    section_num = section_num, 
    headland_length = headland_length,
    side_length = side_length,
    min_plot_length  = min_plot_length, 
    max_plot_length = max_plot_length,
    perpendicular = perpendicular,
    second_input = FALSE 
  )
)) %>% 
mutate(exp_plots = list(
  exp_data$exp_plots
)) %>% 
mutate(ab_lines_data = list(
  exp_data$ab_lines_data
)) %>% 
#=== make ab-lines ===#
mutate(ab_lines = list(
  ab_lines <- make_ab_lines(
    ab_sf = ab_sf,
    ab_lines_data = ab_lines_data,
    base_ab_lines_data = base_ab_lines_data,
    plot_width = input_plot_width, 
    machine_width = machine_width,
    ab_line_type = ab_line_type
  )
)) %>% 
mutate(line_edge = list(
  make_plot_edge_line(
    ab_lines_data = ab_lines_data,
    create_plot_edge_line = create_plot_edge_line,
    base_ab_lines_data = base_ab_lines_data,
    plot_width = input_plot_width
  ) 
))

line_edge <- trial_data_first$line_edge[[1]]

trial_data_first <- dplyr::select(trial_data_first, - line_edge)

#/*=================================================*/
#' # Second input two-input case
#/*=================================================*/
if (num_unique_plot_width == 1 & nrow(trial_data_pa) == 1) {
  #=== one-input case ===#
  trial_data_e <- trial_data_first 

} else if(num_unique_plot_width == 1 & nrow(trial_data_pa) == 2) {
  #=== two-input case, but the same plot width for both inputs ===#
  trial_data_second <- 
  trial_data_pa[2, ] %>% 
  mutate(base_ab_lines_data = list(
    prepare_ablines(
      ab_line = ifelse(
        ab_line_type == "lock",
        st_as_sf(ab_sf), # ab-sf provided 
        st_as_sf(line_edge) # the edge of the experiment plots of the first input 
      ) %>% .[[1]], 
      field = field_sf, 
      plot_width = input_plot_width
    ) 
  )) %>% 
  mutate(exp_data = NA) %>% 
  #=== use the same experiment plots as the first one ===#
  mutate(exp_plots = list(
    trial_data_first$exp_plots[[1]]
  )) %>% 
  #=== use the ab-lines data as the first one ===#
  mutate(ab_lines_data = list(
    trial_data_first$ab_lines_data[[1]]
  )) %>% 
  #=== make ab-lines ===#
  mutate(ab_lines = list(
    ab_lines <- make_ab_lines(
      ab_sf = ab_sf,
      ab_lines_data = ab_lines_data,
      base_ab_lines_data = base_ab_lines_data,
      plot_width = input_plot_width, 
      machine_width = machine_width,
      ab_line_type = ab_line_type
    )
  ))

  trial_data_e <- rbind(trial_data_first, trial_data_second)
  # trial_data_e$exp_plots

} else {

  trial_data_second <- 
  trial_data_pa[2, ] %>% 
  mutate(base_ab_lines_data = list(
    prepare_ablines(
      ab_line = ifelse(
        ab_line_type == "lock",
        st_as_sf(ab_sf), # ab-sf provided 
        st_as_sf(line_edge) # the edge of the experiment plots of the first input 
      ) %>% .[[1]], 
      field = field_sf, 
      plot_width = input_plot_width
    ) 
  )) %>% 
  mutate(exp_data = list(
    make_trial_plots(
      field = field_sf, 
      #--- by default uses the first one ---#
      ab_lines_data = base_ab_lines_data, 
      ab_line_type = ab_line_type,
      plot_width = input_plot_width, 
      machine_width = machine_width, 
      harvester_width = harvester_width, 
      section_num = section_num, 
      headland_length = headland_length,
      side_length = side_length,
      min_plot_length  = min_plot_length, 
      max_plot_length = max_plot_length,
      perpendicular = perpendicular,
      second_input = TRUE
    )
  )) %>% 
  mutate(exp_plots = list(
    exp_data$exp_plots
  )) %>% 
  mutate(ab_lines_data = list(
    exp_data$ab_lines_data
  )) %>% 
  #=== make ab-lines ===#
  mutate(ab_lines = list(
    ab_lines <- make_ab_lines(
      ab_sf = ab_sf,
      ab_lines_data = ab_lines_data,
      base_ab_lines_data = base_ab_lines_data,
      plot_width = input_plot_width, 
      machine_width = machine_width,
      ab_line_type = ab_line_type
    )
  ))

  trial_data_e <- rbind(trial_data_first, trial_data_second)

}

``` 

```{r }

trial_data_eh <-
trial_data_e %>% 
rowwise() %>% 
mutate(ab_lines = list(
  if (!is.null(ab_lines)) {
    st_transform(ab_lines, 4326)
  }
)) %>% 
#=== dissolve the experimental plots as a single polygon ===#
mutate(experiment_plots_dissolved = list(
  exp_plots %>% 
    st_buffer(0.01) %>% # this avoids tiny tiny gaps between plots
    st_snap_to_grid(size = 0.0001) %>%
    st_make_valid() %>% 
    summarize(plot_id = min(plot_id)) 
)) %>% 
#=== Create headland ===#
# experiment_plots_dissolved <- trial_data_eh$experiment_plots_dissolved
# trial_data_eh$headland
mutate(headland = list(
  st_difference(field_sf, experiment_plots_dissolved) %>%
    st_as_sf() %>% 
    rename(., geometry = attr(., "sf_column")) %>% 
    dplyr::select(geometry)
)) %>% 
mutate(tm_exp_head = list(
  tm_shape(field_sf) +
    tm_borders(col = "black") + 
  tm_shape(headland) +
    tm_fill(
      col = "red", 
      alpha = 0.3, 
      title = "Headland"
    ) +
  tm_shape(exp_plots) +
    tm_fill(
      col = "strip_id", 
      palette = "Spectral", 
      style = "order"
    )  +
  tm_shape(field_sf) +
    tm_borders() +
  tm_layout_to_add 
))

```



```{r }
trial_data_eh$tm_exp_head

```

## Save experiment plots and headland 

This object can be used when debugging the subsequent parts. 

```{r }
saveRDS(
  trial_data_eh,
  here("Data", "Growers", ffy, "TrialDesign", "exp_plots.rds")
)  
```


# Assign rates

## Assigning rates

```{r }

if (nrow(trial_data) > 1) {

  trial_data_eh$push <- c(FALSE, TRUE)

} else {

  trial_data_eh$push <- FALSE

}

#=== user-specified number of levels ===#
# data_sf <- trial_data_r$exp_plots[[1]]
# design_type <- trial_data_r$design_type[[1]]
# max_jump <- trial_data_r$max_jump[[1]]
# gc_rate <- round(trial_data_r$gc_rate[[1]])
# min_rate <- trial_data_r$min_rate[[1]]
# max_rate <- trial_data_r$max_rate[[1]]
# num_levels <- trial_data_r$num_levels [[1]]# ignored
# rates <- trial_data_r$rates[[1]]
# push <- trial_data_r$push[[1]]

trial_data_r <- trial_data_eh %>% 
  mutate(experiment_design = list(
    assign_rates(
      data_sf = exp_plots,
      design_type = design_type,
      max_jump = max_jump, # ignored if rates specified
      gc_rate = round(gc_rate), # ignored if rates specified
      min_rate = min_rate, # ignored if rates specified
      max_rate = max_rate, # ignored if rates specified
      num_levels = num_levels, # ignored if rates specified
      rates = rates,
      push = push,
    ) %>% 
    dplyr::select(rate)
  )) %>% 
  mutate(headland = list(
    mutate(headland, rate = round(gc_rate)) %>% 
    dplyr::select(rate)
  )) %>% 
  mutate(input_type = list(
    case_when(
      form == "seed" ~ "S",
      form %in% c("uan28", "uan32", "urea", "NH3") ~ "N",
      #=== needs to change this ===#
      form == c("potash") ~ "K",
      form == "chlorine" ~ "C",
      form == "boron" ~ "B"
    )
  )) %>% 
  mutate(trial_design = list(
    rbind(
      experiment_design,
      headland
    ) %>% 
    #=== only for mapping ===#
    mutate(rate_tm = factor(rate)) %>% 
    setnames(
      "rate",
      case_when(
        form == "seed" ~ "tgts_K",
        form %in% c("uan28", "uan32", "urea", "NH3") ~ "tgtn",
        #=== needs to change this ===#
        form == c("potash") ~ "tgtk",
        form == "chlorine" ~ "C",
        form == "boron" ~ "B"
      )
    ) %>% 
    st_transform(4326) 
  )) %>% 
  mutate(trial_design = list(
    if ("tgts_K" %in% names(trial_design)) {
      mutate(trial_design, tgts = trial_design$tgts_K * 1000) %>% 
        relocate(tgts_K, tgts)
    } else {
      trial_design
    }
  )) %>% 
  dplyr::select(
    - exp_plots, - experiment_plots_dissolved,
    - headland, - tm_exp_head, - experiment_design
  ) %>% 
  mutate(design_summary = list(
    trial_design %>% 
    mutate(area = as.numeric(st_area(.))) %>% 
    mutate(acres = area * 0.000247105) %>% 
    data.table()%>% 
    .[, .(
      tot_input = sum(acres * as.numeric(as.character(rate_tm))),
      tot_acres = sum(acres)
    )]  
  ))  

``` 

# Trial Design Maps

```{r }
trial_data_r %>% 
mutate(map_design_temp = list(
  tm_shape(trial_design) +
  tm_polygons(
    col = "rate_tm",
    title = form,
    palette = ifelse(form == "seed", "Greens", "Reds")
  ) +
  tm_layout(
    title = paste0(
      "Total Input = ", round(design_summary[, tot_input]), 
      "\nAcres = ", round(design_summary[, tot_acres], digits = 2)
    )
  ) +
  tm_layout_to_add 
)) %>% 
mutate(map_design = list(
  if (ab_line_type == "non") {
    map_design <- map_design_temp
  } else {
    map_design <- 
    map_design_temp + 
    tm_shape(ab_lines) +
    tm_lines(
      col = "ab_id",
      palette = "Dark2",
      lwd = 2
    ) 
  }
)) %>% 
pluck("map_design")
  
```

## Check the plot alignment when two-input case

```{r }
if (nrow(trial_data_r) > 1) {
  designs <- trial_data_r$trial_design 
  tm_shape(designs[[1]]) +
    tm_borders(col = "blue") +
  tm_shape(designs[[2]]) +
    tm_borders(col = "red")
}
```

# Save the trial design

```{r }
file_name_append <- "_file-name-append-here_"

# time_user <- paste0(
#   Sys.time(), 
#   "-",
#   Sys.getenv("USER")
# ) %>% 
# gsub(" ", "-", .) %>% 
# gsub("_", "-", .)  

dsn_name <- here("Data", "Growers", ffy, "TrialDesign")

#=== save as rds ===#
saveRDS(
  trial_data_r,
  here("Data", "Growers", ffy, "TrialDesign/trial_design.rds")
)

#=== write the trial design as a shape file ===#
trial_data_r %>% 
summarise(list(
  st_write(
    trial_design %>% dplyr::select(- rate_tm), 
    dsn = dsn_name,
    layer = paste0(
      "trial-design-", tolower(input_type), 
      "-", year,  
      ifelse(is.na(line_edge_id), "", paste0("-", line_edge_id)),
      ifelse(is.na(file_name_append), "", paste0("-", file_name_append)) 
    ),
    driver = "ESRI Shapefile",
    append = FALSE
  )
)) 

#=== write the ab-lines as a shape file ===#
trial_data_r %>% 
summarise(list(
  if (ab_line_type != "non") {
    st_write(
      ab_lines, 
      dsn = dsn_name,
      layer = paste0(
        "ab-lines-farmer-", tolower(input_type), 
        "-", year,  
        ifelse(is.na(line_edge_id), "", paste0("-", line_edge_id)),
        ifelse(is.na(file_name_append), "", paste0("-", file_name_append)) 
      ),
      driver = "ESRI Shapefile",
      append = FALSE
    )
  } else {
    NULL
  }
)) 

```


