---
title: "Run Analysis for A crop-type-here Experiment"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: true
    number_sections: true
---

# Preparation

## Set up

```{r setup, cache = F, echo = F}
library(knitr)
knitr::opts_chunk$set(
  cache = TRUE,
  echo = TRUE,
  error = TRUE,
  warning = FALSE,
  fig.retina = 6,
  message = FALSE
)

options(knitr.duplicate.label = "allow")

#--- working field-year ---#
ffy <- "field-year-here" 

#--- root directory ---#
opts_knit$set(root.dir = here("Data", "Growers", ffy))

```

## Packages

```{r pacakges, cache = FALSE}
# === packages ===#
library(sf)
library(tmap)
library(mgcv)
library(ggcorrplot)
library(R.utils)
library(patchwork)
library(scam)
library(parallel)
library(dplyr)
library(tidyverse)
library(corrplot)
library(data.table)
library(GWmodel)
library(mgcv)

```

```{r map-layout, cache = TRUE}
tm_layout_to_add <- tm_layout(
  legend.outside = "TRUE",
  frame = FALSE,
  legend.title.size = 2,
  legend.text.size = 1.5
)

```

## Parameters and functions

```{r echo = F, results = "hide"}
#/*----------------------------------*/
#' ### Trial parameters
#/*----------------------------------*/
# source(here("Codes/Functions/unpack_field_parameters.R"))
source(
  get_r_file_name("Functions/unpack_field_parameters.R"), 
  local = TRUE
)

crop_price_table <- fread(here("Data/CommonData/CropPrice.csv")) %>% 
  setnames(names(.), tolower(names(.))) %>% 
  filter(type == "current") %>% 
  rename(crop_price = price)

input_price_table <- fread(here("Data/CommonData/InputPrice.csv")) %>% 
  setnames(names(.), tolower(names(.)))

#/*~~~~~~~~~~~~~~~~~~~~~~*/
#' ### variable name dictionary
#/*~~~~~~~~~~~~~~~~~~~~~~*/
dictionary <- fromJSON(
  file.path(
    here("Data", "CommonData"),
    "variable_name_dictionary.json"
  ),
  flatten = TRUE
) %>% 
data.table()

#/*----------------------------------*/
#' ### Source functions
#/*----------------------------------*/
source(
  "https://github.com/tmieno2/DIFM/blob/master/Functions/prepare.R?raw=TRUE",
  local = TRUE
)


```

# Title-here analysis

## Read the analysis data 

```{r data-prep-s, cache = F, results = "hide"}

data_sf <- here("Data/Growers", ffy, "Analysis-Ready/analysis_data.rds") %>% 
  readRDS() %>% 
  rename(yield = yield_vol) %>% 
  setnames(names(.), tolower(names(.))) %>% 
  filter(!is.na(yield)) %>% 
  cbind(., st_coordinates(st_centroid(.))) 

```

## GWR estimation for management zone delineation

### GWR estimation

```{r gwr, results = "hide"}

analysis_res_g <- trial_info %>% 
  left_join(crop_price_table, by = "crop") %>% 
  mutate(data = rep(list(data_sf), nrow(.))) %>% 
  rowwise() %>% 
  mutate(
    data = list(
      setnames(
        data.table::copy(data),
        paste0(tolower(input_type), "_rate"),
        "input_rate"
      )
    )
  ) %>%  
  mutate(
    field_vars = list(
      find_field_vars(data)
    )
  ) %>% 
  mutate(
    data = list(
      gen_y_res(data, field_vars)
    )
  ) %>% 
  mutate(
    data = list(
      run_gwr(subset(data, input_rate != 0), "input_rate")  
    )
  ) 

```

### GWR estimates histogram

```{r }
pluck(analysis_res_g, "data") %>% 
  map(., ~ 
    ggplot(.) +
      geom_histogram(
        aes(x = b_slope), 
        color = "blue", 
        fill = "white"
      )
  )

```

### Define management zones based on GWR

```{r yield-response-functions-by-group}

# data.table(analysis_res$data[[1]])[, sum(is.na(clay))]

analysis_res_m <- analysis_res_g %>% 
  mutate(
    data = list(
      define_mz(
        data = data, 
        max_num_zones = 4, 
        min_obs = 300
      ) 
    )
  )
  
```

```{r }

pluck(analysis_res_m, "data") %>% 
  map(., ~ 
    tm_shape(.) +
    tm_fill(col = "zone_txt", palette = "Set1") +
    tm_layout_to_add
  )

```

## Yield response function (GAM) estimation by zone

```{r gam-estimate}

analysis_res_gam <- analysis_res_m %>% 
  mutate(gam_res = list(
    run_scam_gam(data = data, field_vars = field_vars)
  )) 
  # %>% 
  # #=== make the observations in the same zone have the same X and Y ===#
  # mutate(
  #   data = list(
  #     data.table(data) %>% 
  #       .[, `:=`(
  #         X = mean(X), 
  #         Y = mean(Y)
  #       ), by = "zone_txt"] %>% 
  #       st_as_sf()
  #   )
  # )

```

Here is the `gam` model formula:

```{r }
analysis_res_gam$gam_res

```


## Profit estimation and economic optimization

```{r }

analysis_res_e <- analysis_res_gam %>% 
  #=== single average observation by zone ===#
  mutate(data_for_eval = list(
    make_data_for_eval(
      data = data,
      est = gam_res
    )
  )) %>% 
  #=== input rate sequence by zone to be tested ===#
  mutate(input_rate_seq = list(
    data.table(data)[, .(
      input_rate = seq(
        quantile(input_rate, 0.025),
        quantile(input_rate, 0.975),
        length = 100
      )
    ),
    by = zone_txt]
  )) %>% 
  #=== predict yield values at different input rates ===#
  mutate(eval_data = list(
    predict_yield_range(
      data_for_eval = data_for_eval, 
      input_rate_seq = input_rate_seq,
      est = gam_res
    ) %>% 
    .[, type := "opt_v"]%>% 
    .[, .(
      input_rate, zone_txt, type, yield_hat, yield_hat_se
    )]
  )) %>% 
  #=== Adjust yield values to match up with actual yields (this is purely for figures below) ===#
  mutate(
    #=== mean predicted yield ===#
    mean_yield_hat_opt = 
    list(
      eval_data[, .(mean_yield_hat = mean(yield_hat)), by = zone_txt]
    ), 
    #=== mean actual yield by zone ===#
    mean_yield_actual = 
    list(
      data.table(data)[, 
      .(mean_yield_actual = mean(yield)), 
      by = zone_txt
      ]
    ),
    #=== shift yield so that figures look ===#
    yield_shift_opt = 
    list(
      mean_yield_actual[mean_yield_hat_opt, on = "zone_txt"] %>% 
        .[, yield_shift :=  mean_yield_actual - mean_yield_hat] %>% 
        .[, .(zone_txt, yield_shift)]
    ),
    eval_data = 
    list(
      eval_data %>% 
      yield_shift_opt[., on = "zone_txt"] %>% 
      .[, yield_hat := yield_hat + yield_shift] %>% 
      .[, profit_hat := crop_price * yield_hat - price * input_rate] %>% 
      .[, profit_hat_se := crop_price * yield_hat_se] 
    )
  ) %>% 
  dplyr::select(
    - mean_yield_hat_opt, 
    - yield_shift_opt, 
    - mean_yield_actual
  ) %>% 
  mutate(opt_input_data = list(
   opt_input_data <- eval_data %>% 
    .[, .SD[profit_hat == max(profit_hat), ], by = zone_txt] %>% 
    setnames("input_rate", "opt_input") 
  )) %>% 
  #=== assign optimal variable input rate to the data ===#
  mutate(data = list(
    left_join(
      data, 
      opt_input_data,
      by = "zone_txt"
    )
  )) %>% 
  #=== find the optimal uniform rate ===#
  mutate(data = list(
    mutate(
      data, 
      opt_input_u = find_opt_u(
        data = data, 
        gam_res = gam_res,
        crop_price = crop_price,
        input_price = price
      )
    )
  ))

```

### Yield response functions by zone

```{r }

analysis_res_e %>% 
  mutate(
    ymin = eval_data[, min(yield_hat - 1.96 * yield_hat_se)] - 10
  ) %>% 
  dplyr::select("data", "eval_data", "ymin") %>% 
  mutate(g_ys = 
    list(
      eval_data %>% 
      filter(type == "opt_v") %>% 
      ggplot(data = .) +
      geom_line(aes(y = yield_hat, x = input_rate)) +
      geom_ribbon(
        aes(
          ymin = yield_hat - 1.96 * yield_hat_se, 
          ymax = yield_hat + 1.96 * yield_hat_se, 
          x = input_rate
        ),
        fill = "red",
        alpha = 0.4
      ) +
      geom_point(
        data = data, 
        aes(
          y = yield, 
          x = input_rate
        ),
        size = 0.4
      ) +
      facet_grid(. ~ zone_txt) +
      ylim(ymin, NA)
    )
  ) %>% 
  pluck("g_ys")
  
```

## Testing Profitability by Zone

```{r gen-opt-S-v-data-map}

# analysis_res_o$data[[1]]
# analysis_res_o$pi_dif_test_zone
# analysis_res_o$opt_gc_data
# analysis_res_o$data[[1]] %>% data.table %>% 
#   .[, mean(yield), by = zone_txt] 

analysis_res_o <- analysis_res_e %>% 
  #=== Assign gc_rate for all the observations ===#
  mutate(data = list(
    assign_gc_rate(data, input_type, gc_type, gc_rate)
  )) %>% 
  #=== Test the statistical sig for profit differential by zone ===#
  mutate(pi_dif_test_zone = list(
    get_dif_stat_zone(
      data = data.table(data), 
      test_var = "input_rate", 
      opt_var = "opt_input",
      gc_var = "gc_rate",
      gam_res = gam_res,
      by_var = "zone_txt",
      crop_price = crop_price,
      input_price = price
    )
  )) %>% 
  mutate(opt_gc_data = list(
    get_opt_gc_data(
      data = data,
      pi_dif_test_zone = pi_dif_test_zone,
      opt_input_data = opt_input_data
    )
  ))

```

```{r }
analysis_res_o$pi_dif_test_zone 
analysis_res_o$opt_gc_data 
``` 

### Optimal vs GC (profit difference for individual observations)

```{r }
analysis_res_og <- analysis_res_o %>% 
  mutate(
    pi_indiv_opt = list(
      predict_yield(
        data = data, 
        est = gam_res, 
        var_name = "opt_input"
      ) %>% 
      data.table() %>% 
      .[, .(yield_hat, obs_id, input_rate)] %>% 
      .[, pi_hat_opt := crop_price * yield_hat - price * input_rate]
    ),
    pi_indiv_gc = list(
      predict_yield(
        data = data, 
        est = gam_res, 
        var_name = "gc_rate"
      ) %>% 
      data.table() %>% 
      .[, .(yield_hat, obs_id, input_rate)] %>% 
      .[, pi_hat_gc := crop_price * yield_hat - price * input_rate]
    ),
    pi_dif = list(
      left_join(
        pi_indiv_opt, 
        pi_indiv_gc,
        by = "obs_id"
      ) %>% 
      mutate(
        pi_dif = pi_hat_opt - pi_hat_gc
      )
    ),
    data = list(
      left_join(data, pi_dif, by = "obs_id"
    ))
  ) %>% 
  dplyr::select(
    - pi_indiv_opt, 
    - pi_indiv_gc, 
    - pi_dif
  )

```

### Whole-field profit

```{r }

# analysis_res_w$whole_profits_test

analysis_res_w <- analysis_res_og %>% 
  mutate(whole_profits_test = list(
    get_whole_pi_test(
      data = data, 
      gam_res = gam_res, 
      crop_price = crop_price,
      input_price = price
    )
  )) 

```

```{r }
analysis_res_w$whole_profits_test
```

## Get correlations between b_slope and soil/field characteristics and create figures of interactions

```{r }
analysis_res_ch <- analysis_res_w %>% 
  mutate(field_interactions = list(
      get_field_int(data, field_vars)
  )) %>% 
  mutate(field_plots = list(
    get_inteactions_maps_ys(data, input_type, field_interactions)
  ))

```

```{r }
analysis_res_ch$field_interactions
``` 

## Save the results

```{r }
analysis_res_f <- analysis_res_ch %>% 
  dplyr::select(
    - gam_res
  ) %>% 
  mutate(
    crop_price = crop_price
  )

file_name <- here(
  "Reports/Growers", 
  ffy, 
  "analysis_results.rds" 
)

saveRDS(analysis_res_f, file_name)

```

```{r eval = F}
# analysis_res_f$field_plots[[1]]$g_ys_char
# analysis_res_f <- readRDS(file_name)
 
```

